---
title: "Initial Steps to Network Analysis"
subtitle: "Exploring ISIS Fanboy Tweets"

author: Fadi Egho
output: html_notebook
---


  Fifth Tribe, a digital agency serving non-profits and government agencies, has scraped over 17,000 tweets from 107 ISIS-supporting twitter users from September of 2015 till January of 2016 (roughly corresponding to ISIS’ peak notoriety period) and uploaded them onto [kaggle]('https://www.kaggle.com/fifthtribe/how-isis-uses-twitter') as a public domain dataset [^1]. Let's start by loading some necessary packages:
  
```{r setup, echo=T}
library(readxl)
library(tidyverse)
library(stringi)
```

We then import the data set from excel:
```{r}
twtr <- read_excel('../S580/tweets.xlsx')
head(twtr)
glimpse(twtr)
```
As noted above, the data set captures variables such as the *username*, *followers*, *time*, and *tweets* (where the text in each tweet also contains ‘mentions’ of other users).

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.


[^1]: Fifth Tribe. (2016, May). How ISIS Uses Twitter, Version 2. Retrieved February 19, 2020 from 'https://www.kaggle.com/fifthtribe/how-isis-uses-twitter'